---
title: "Advanced_Data_Visualization"
author: "Sanghyeon-Han"
date: "2025-06-04"
output: html_document
---

https://github.com/Sanghyeon-Han/ENVS-193DS_homework-03.git

```{r setup}
# Load required libraries
library(tidyverse)
library(here)
library(gt)
library(janitor)
library(readxl)
library(ggplot2)
library(dplyr)
library(readr)
library(patchwork)
library(scales)
```

# Load custom Google font
``{r}
font_add_google("Lato", "lato")
showtext_auto()
```

# Load the data
```{r}
data <- read_csv(here("data", "personal_data.csv"))
```

#Creating Visualization1
```{r}
p1 <- ggplot(data, aes(x = day, y = steps, fill = is_weekend)) +
  geom_col() +
  labs(title = "Steps per Day", x = "Day", y = "Steps") +
  theme_minimal()

p1  # <- This will actually display the plot
```


```{r}
# Creating Visualization1
p1 <- ggplot(data, aes(x = date, y = hours_sleep)) +
  geom_line(color = "#0073C2", size = 1.2) +
  geom_point(size = 2) +
  labs(
    title = "Sleep Over Time",
    subtitle = "Tracking my sleep hours day by day",
    x = "Date", y = "Hours Slept"
  ) +
  theme_minimal(base_family = "lato")

p1  # <- This will display the plot

```

```{r}
# Creating Visualization2
library(waffle)

mood_counts <- data %>%
  count(mood)

library(scales)  # for hue_pal()

p2 <- waffle(mood_counts, rows = 5,
             title = "Mood Distribution",
             colors = hue_pal()(nrow(mood_counts)))


p2  # <- This will display the waffle chart
```
